---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

```{r upload libraries, echo=FALSE, message=FALSE}
library(devtools)
```



# graph


The `graph` package was created to complete the [Assignment B-2](https://stat545.stat.ubc.ca/assignments/assignment-b2/), for the [STAT545b 2021 course](https://stat545.stat.ubc.ca/).


## Overview

`graph` is a package based in ggplot2 developed to facilitate the creation of histograms to explore the distribution of variables. The function `histogram()` displays the distribution of a single numeric variable through a histogram.


## Installation

`graph` is not yet on CRAN, but you can install the package from GitHub using the following code:


```{r, message=FALSE}
devtools::install_github("cataralina/graph")
```

## Usage

The package have one function that displays the distribution of a single numeric variable
through a histogram:

+ `histogram()`

You start with `histogram()`, and then supply a dataset and the numeric variable to plot. Information about the xlab tittle, the number of bins and what to do with the NA is optional, but you can specify it using:


+ `xlab = "title"`    
+ `bins =` number of bins (defaults to **30**)    
+ `na.rm =` A logical vector indicating whether NA values should be stripped before the computation proceeds. **TRUE** is the default.


## Example


```{r Load packages}
library(graph)
library(gapminder)
```

```{r example}
histogram(gapminder, lifeExp)
```

```{r}
histogram(gapminder, lifeExp, xlab = "Life Expectancy")
```

```{r}
histogram(gapminder, gdpPercap, xlab = "GDP per capita", bins = 20)
```

